Excitonic Energy Transfer Couplings at Short Distances: Efficient Transfer-Integral Fragmentation Approach Based on Effective One-Electron Operators

### 2019-08-28 papers/3_eet.I.Theory/paper-r0.tex
Equations of OEP matrices updated

$\Delta E^X_{e\rightarrow g}(Y)$ accounts for the environmental effect due to other molecule,

@@

   \frac{\phi_i^*({\bf r}_1 \phi_j({\bf r}_1 
                 \phi_j^*({\bf r}_2 \phi_i({\bf r}_2)}{\vert {\bf r}_1 - {\bf r}_2 \vert}

@@

 \cong \sum_{\xi\in A}^{\rm DF} \bra{\xi} V^{A,{\rm ET1}}_{\xi,HL}

@@

 \mathscr{F}_0^B \ket{\phi_L^B} \cong \sum_{\eta\in B}^{\rm DF} V^{B,{\rm ET1}}_{\eta,L} \ket{\eta} 

@@

$V^{A,{\rm ET1}}_{\xi,HL}$ and $V^{B,{\rm ET1}}_{\eta,L}$

@@

 \sum_{\xi\in A}^{\rm DF} S_{\xi L}^{AB} V^{A,{\rm ET1}}_{\xi,HL} +
 \sum_{\eta\in B}^{\rm DF} S_{\eta L}^{BA} V^{B,{\rm ET1}}_{\eta,L}

@@

$A$ and $B$ are necessary to compute, i.e.,

@@

and $C_{\beta U}^Y$ is the SCF LCAO-MO matrix for isolated molecule $Y$.

@@

 \sum_{\eta\in B}^{\rm DF} S_{\eta L}^{BA} V^{B,{\rm ET1}}_{\eta,HL} +
 \sum_{\xi\in A}^{\rm DF} S_{\xi L}^{AB} V^{A,{\rm ET1}}_{\xi,L}

@@

Similar considerations apply to the hole transfer (HT) matrix elements.
The expression
%
\begin{multline}\label{e:v0-ht1}
 V^{{\rm HT1},(0)} \equiv \left< \Phi_1 \vert \mathscr{H} \vert \Phi_4 \right> \approx 
 t_{H\rightarrow L}^A \times \Big\{ 
-\big(\phi_H^A \big| \mathscr{F} \big| \phi_H^B \big) \\
   + 2 \big( \phi_H^A \phi_L^A \big| \phi_L^A \phi_H^B \big) - \big( \phi_H^A \phi_H^B \big| \phi_L^A \phi_L^A \big) 
 \Big\} 
\end{multline}
%
can be recast as
%
\begin{multline}\label{e:v0-ht1-oep}
 V^{{\rm HT1},(0)} \cong t_{H\rightarrow L}^A \Big\{ 
 \sum_{\xi\in A}^{\rm DF} S_{\xi H}^{AB} V^{A,{\rm HT1}}_{\xi,HL} +
 \sum_{\eta\in B}^{\rm DF} S_{\eta H}^{BA} V^{B,{\rm HT1}}_{\eta,H}
 \Big\} \;,
\end{multline}
%
with the effective potential matrices given by
%
%
\begin{subequations}
\begin{align}
 \bra{\phi_H^A} \left\{ -\mathscr{F}_0^A - \hat{v}^A_{LL} \right\}
 + \bra{\phi_L^A} 2 \hat{v}^A_{HL} 
 &\cong \sum_{\xi\in A}^{\rm DF} \bra{\xi} V^{A,{\rm HT1}}_{\xi,HL} \\
 -\mathscr{F}_0^B \ket{\phi_H^B} &\cong \sum_{\eta\in B}^{\rm DF} V^{B,{\rm ET1}}_{\eta,H} \ket{\eta} 
\end{align}
\end{subequations}
%
The twin term HT2 is accordingly
%
\begin{multline}\label{e:v0-ht2-oep}
 V^{{\rm HT2},(0)} \cong t_{H\rightarrow L}^B \Big\{ 
 \sum_{\eta\in B}^{\rm DF} S_{\eta H}^{BA} V^{B,{\rm HT2}}_{\eta,HL} +
 \sum_{\xi\in A}^{\rm DF} S_{\xi H}^{AB} V^{A,{\rm HT2}}_{\xi,H}
 \Big\} \;.
\end{multline}
%
As can be seen, to compute Hamiltonian matrix elements
associated with the electron and hole transfer, eight in total
different OEP matrices need to be pre\hyp{}computed and stored in a file.
Note that each of these matrices is actually just a vector of length
equal to the size of the auxiliary basis set chosen. Therefore,
it can be predicted that the computational cost of evaluation of the OEP\hyp{}based Hamiltonian
matrix elements is negligible as compared to the original TI/CIS method.
In Appendix~\ref{a:gdf-formulae}, explicit working formulae
for the OEP matrix elements are given in terms of the AO's.

@@

The Hamiltonian matrix element that is associated with the charge transfer process
is
%
\begin{equation}\label{e:v0-ct}
 V^{{\rm CT },(0)} = 
     2 \braket{\phi_H^A \phi_L^B}{\phi_L^A \phi_H^B}
      -\braket{\phi_H^A \phi_H^B}{\phi_L^A \phi_L^B}
\end{equation}
%
Since it involves ERI's of type $\braket{AB}{AB}$ OEP's cannot be directly defined here.
However, Mulliken approximation allows one to express ERI's in terms of the
overlap and Coulomb integrals, i.e.,
%
\begin{equation}
 \braket{ij}{kl} \approx \frac{1}{4} S_{ij}S_{kl}
 \left[ \braket{ii}{kk} + \braket{ii}{ll} + \braket{jj}{kk} + \braket{jj}{ll}\right] \;.
\end{equation}
%
Application of the above approximation to Eq.~\eqref{e:v0-ct} yields
%
\begin{multline}\label{e:v0-ct.mulliken}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B}\right] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_H^B \phi_H^B}\right]  \;,
\end{multline}
%
where 
%
\begin{equation} 
 r_{UW}^X \equiv \braket{\phi_U^X \phi_U^X}{\phi_W^X \phi_W^X} \;.
\end{equation}
%
First of all, note that $r_{HL}^A$ and $r_{HL}^B$ are just constant numbers
associated with the isolated monomers and 
independent on the molecular aggregate. Also, the remaining four ERI's
can be considered as Coulombic interactions between HOMO and LUMO orbitals
of unperturbed molecular wavefunctions.
Then, applying distributed multipole expansion and truncating it on the monopole
one finds that
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} \approx \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} \;,
\end{equation}
%
where the charge centroids of HOMO orbitals are given by
%
\begin{equation} 
 {\bf r}_H^X = \tbraket{\phi_H^X}{\hat{\bf r}}{\phi_H^X} \;.
\end{equation}
%
Note that, once occupied molecular orbitals are localized, the above approximation
should yield correct description. LUMO orbitals are usually not much localized.
Here, we use the distributed cumulative atomic charges to represent them, %cite CAMM paper
%
\begin{equation} 
 q^X_{x,L} =-\sum_{\alpha\in x} \sum_\beta S_{\alpha\beta} C_{\alpha L}^X C_{\beta L}^X
\end{equation}
%
and one can find that assuming this one obtains
%
\begin{equation} 
 \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B} 
 \approx \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At}
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \;.
\end{equation}
%
The two remaining ERI's can be then approximated as follows:
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
 \approx -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} \;,
\end{equation}
%
and similarly for the twin ERI. To summarize the derivation, the CT matrix element
is approximately given by
%
\begin{multline}\label{e:v0-ct.mulliken.working}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\ 
 + \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} 
 + \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At} 
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \Big] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\
 -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} 
 -\sum_{x\in A}^{\rm At}
 \frac{q_{x;L}^A}{\vert {\bf r}_H^B - {\bf r}_x \vert} \Big]\;.
\end{multline}
%

@@

Mulliken approximation can also be used to treat the pure exchange coupling (Eq.).
It is straightforward to show that
%
\begin{multline}\label{e:v0-exch-mulliken}
V^{{\rm Exch},(0)} \approx -\frac{1}{8} \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
 P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
 S_{\mu\lambda}  S_{\sigma\nu} \times \\
 \left[ \braket{\mu\mu}{\sigma\sigma} + \braket{\lambda\lambda}{\nu\nu} 
      + \braket{\mu\mu}{\nu\nu} + \braket{\lambda\lambda}{\sigma\sigma}\right] \;.
\end{multline}
%
However, ERI's that involve AO's in two different molecules can be safely neglected.
That leads to the following simplified expression:
%
\begin{multline}\label{e:v0-exch.mulliken.working}
V^{{\rm Exch},(0)} \approx 
  -\frac{1}{8} \Big\{ \sum_{\mu\nu\in A} P_{\nu\mu}^{g\rightarrow e(A)} G_{\mu\nu}^A
    [{\bf s}^{AB} {\bf P}^{g\rightarrow e(B)} {\bf s}^{BA} ]_{\mu\nu} \\
  + \sum_{\sigma\lambda\in B} P_{\lambda\sigma}^{g\rightarrow e(B)} G_{\lambda\sigma}^B
    [{\bf s}^{BA} {\bf P}^{g\rightarrow e(A)} {\bf s}^{AB} ]_{\sigma\lambda} 
  \Big\}
\end{multline}
%
with $G_{\mu\nu} \equiv \braket{\mu\mu}{\nu\nu}$. Note that $G_{\mu\nu}^A$ and $G_{\lambda\sigma}^B$
are just constant matrices that can be considered as effective fragment potentials.

@@

To summarize, the overall form of the OEP-TI/CIS model is still given as in the original TI/CIS model
by
%
\begin{equation}
  V \approx V^{\rm Direct} + V^{\rm Inirect} \;,
\end{equation}
%
where the so called `direct' and `indirect' coupling constants are respectively
%
\begin{subequations}
\begin{align}
  V^{\rm Direct  } &\equiv V^{\rm Coul} + V^{\rm Exch} + V^{\rm Ovrl} \;,\\
  V^{\rm Indirect} &\equiv V^{\rm TI-2} + V^{\rm TI-3} \;,
\end{align}
\end{subequations}
%
with
%
\begin{subequations}
\begin{align}
 V^{\rm TI-2} &\equiv-\frac{V^{\rm ET1} V^{\rm HT2}}{E_3-E_1} -\frac{V^{\rm ET2} V^{\rm HT1}}{E_4-E_1}  \;,\\
 V^{\rm TI-3} &\equiv \frac{V^{\rm CT} \left( V^{\rm ET1} V^{\rm ET2} + V^{\rm HT1} V^{\rm HT2}\right) }{(E_3-E_1)(E_4-E_1)} \;.
\end{align}
\end{subequations}
%
However, 
the differences between the original Fujimoto's model and the newly derived OEP\hyp{}based model 
are: 
%
\begin{enumerate}
 \item The Hamiltonian matrix elements are evaluated from the fragment effective 
parameters, for which only the one\hyp{}electron integrals are needed. Therefore, the computational
cost is significantly reduced as compared to the parent TI/CIS model. In particular, 
$V^{\rm Coul}$ is evaluated by using the TrCAMM method developed previously,
$V^{\rm Exch}$ and $V^{\rm CT}$ are computed from the Mulliken approximated
formulae in Eqs.~\eqref{e:v0-exch.mulliken.working}, and \eqref{e:v0-ct.mulliken.working}, respectively,
as well as $V^{\rm ET1}$, $V^{\rm ET2}$,
$V^{\rm HT1}$ and $V^{\rm HT2}$ are treated by the generalized density fitting
with OEP effective matrices as effective parameters spanned in auxiliary AO basis set 
(Eqs.~\eqref{e:v0-et1-oep}, \eqref{e:v0-et2-oep}, \eqref{e:v0-ht1-oep}, \eqref{e:v0-ht2-oep}
and Eqs.~\eqref{e:a:voep}-\eqref{e:a:aoep}); 
 \item The relaxation effects due to the intermolecular interactions are not included
in the current OEP\hyp{}based model.
Note that in the original TI/CIS model the basis states and all the one\hyp{}particle density matrices are built from the
self\hyp{}consistently adjusted fragment densities according to the DFI method.
\end{enumerate}
%
\paragraph*{Overlap corrections to the Hamiltonian.}
Since in the TI/CIS method the basis states are constructed from the monomer wavefunctions,
the overlap effects should be properly taken into account. It was reported previously
that overlap correction to the $\left< \Phi_1 \vert \mathscr{H} \vert \Phi_2 \right>$ 
matrix element brings negligible contributions to the 
total EET coupling (c.f. the `overlap' contribution in Ref.). On the other hand,
the importance of the overlap effects on the other off\hyp{}diagonal Hamiltonian matrix elements were not directly studied. 
After the overlap correction, the constituents of the direct coupling take the form
%
\begin{subequations}\label{e:ovrl-direct}
\begin{align}
 V^{\rm Coul} &= \frac{V^{{\rm Coul},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Exch} &= \frac{V^{{\rm Exch},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Ovrl} &=-\frac{(E_1+E_2)S_{12}}{2(1-S_{12}^2)}   \;.
\end{align}
\end{subequations}
%
The overlap\hyp{}corrected ET, HT and CT matrix elements read
%
\begin{equation}\label{e:ovrl-indirect}
 V^{\rm t} = \left[ 1 - S_{\rm t}^2 \right]^{-1} \left\{ V^{{\rm t},(0)} - \frac{1}{2} (E_1+E_2) S_{\rm t} \right\} \;,
\end{equation}
%
where `t' denotes one of the matrix element types (ET1, ET2, HT1, HT2, CT) 
and $S_{\rm t}$ is the appropriate overlap integral between basis states.
Since evaluation
of Eqs.~\eqref{e:ovrl-direct} and \eqref{e:ovrl-indirect} 
is computationally inexpensive, we shall consider the overlap\hyp{}corrected
Hamiltonian in the present work.

>>>>

$\Delta E^X_{e\rightarrow g}(Y)$ accounts for the environmental effect due to the other molecule,

@@

   \frac{\phi_i^*({\bf r}_1) \phi_j({\bf r}_1)
                 \phi_j^*({\bf r}_2) \phi_i({\bf r}_2)}{\vert {\bf r}_1 - {\bf r}_2 \vert}

@@

 \cong \sum_{\xi\in A}^{\rm DF} \bra{\xi} V^{A;{\rm ET}}_{\xi;HL}

@@

 \mathscr{F}_0^B \ket{\phi_L^B} \cong \sum_{\eta\in B}^{\rm DF} V^{B;{\rm ET}}_{\eta;L} \ket{\eta} 

@@

$V^{A;{\rm ET}}_{\xi;HL}$ and $V^{B;{\rm ET}}_{\eta;L}$

@@

 \sum_{\xi\in A}^{\rm DF} S_{\xi L}^{AB} V^{A;{\rm ET}}_{\xi;HL} +
 \sum_{\eta\in B}^{\rm DF} S_{\eta L}^{BA} V^{B;{\rm ET}}_{\eta;L}

@@

$A$ and $B$ are necessary to be computed, i.e.,

@@

and $C_{\beta U}^X$ is the SCF LCAO-MO matrix for isolated molecule $X$.

@@

 \sum_{\eta\in B}^{\rm DF} S_{\eta L}^{BA} V^{B;{\rm ET}}_{\eta;HL} +
 \sum_{\xi\in A}^{\rm DF} S_{\xi L}^{AB} V^{A;{\rm ET}}_{\xi;L}

@@

Note that OEP matrices for ET1 and ET2 terms share similar structure.
Therefore a joint superscript `ET' is used here to label the OEP matrices
and additional subscripts
$L$ and $HL$ denote the dependence on only LUMO and on both LUMO and HOMO orbitals, respectively.

Similar considerations apply to the hole transfer (HT) matrix elements.
The expression
%
\begin{multline}\label{e:v0-ht1}
 V^{{\rm HT1},(0)} \equiv \left< \Phi_1 \vert \mathscr{H} \vert \Phi_4 \right> \approx 
 t_{H\rightarrow L}^A \times \Big\{ 
-\big(\phi_H^A \big| \mathscr{F} \big| \phi_H^B \big) \\
   + 2 \big( \phi_H^A \phi_L^A \big| \phi_L^A \phi_H^B \big) - \big( \phi_H^A \phi_H^B \big| \phi_L^A \phi_L^A \big) 
 \Big\} 
\end{multline}
%
can be recast as
%
\begin{multline}\label{e:v0-ht1-oep}
 V^{{\rm HT1},(0)} \cong t_{H\rightarrow L}^A \Big\{ 
 \sum_{\xi\in A}^{\rm DF} S_{\xi H}^{AB} V^{A;{\rm HT}}_{\xi;HL} +
 \sum_{\eta\in B}^{\rm DF} S_{\eta H}^{BA} V^{B;{\rm HT}}_{\eta;H}
 \Big\} \;,
\end{multline}
%
with the effective potential matrices given by
%
%
\begin{subequations}
\begin{align}
 \bra{\phi_H^A} \left\{ -\mathscr{F}_0^A - \hat{v}^A_{LL} \right\}
 + \bra{\phi_L^A} 2 \hat{v}^A_{HL} 
 &\cong \sum_{\xi\in A}^{\rm DF} \bra{\xi} V^{A,{\rm HT}}_{\xi,HL} \\
 -\mathscr{F}_0^B \ket{\phi_H^B} &\cong \sum_{\eta\in B}^{\rm DF} V^{B,{\rm HT}}_{\eta,H} \ket{\eta} 
\end{align}
\end{subequations}
%
The twin term HT2 is accordingly
%
\begin{multline}\label{e:v0-ht2-oep}
 V^{{\rm HT2},(0)} \cong t_{H\rightarrow L}^B \Big\{ 
 \sum_{\eta\in B}^{\rm DF} S_{\eta H}^{BA} V^{B;{\rm HT}}_{\eta;HL} +
 \sum_{\xi\in A}^{\rm DF} S_{\xi H}^{AB} V^{A;{\rm HT}}_{\xi;H}
 \Big\} \;.
\end{multline}
%
As can be seen, to compute Hamiltonian matrix elements
associated with the electron and hole transfer, eight in total
different OEP matrices need to be pre\hyp{}computed and stored in a file.
Note that each of these matrices is actually just a vector of length
equal to the size of the auxiliary basis set chosen. Therefore,
it can be predicted that the computational cost of evaluation of the OEP\hyp{}based Hamiltonian
matrix elements is negligible as compared to the original TI/CIS method.
In Appendix~\ref{a:gdf-formulae}, explicit working formulae
for the OEP matrix elements are given in terms of the AO's.

@@

The Hamiltonian matrix element that is associated with the charge transfer process
is
%
\begin{equation}\label{e:v0-ct}
 V^{{\rm CT },(0)} = 
     2 \braket{\phi_H^A \phi_L^B}{\phi_L^A \phi_H^B}
      -\braket{\phi_H^A \phi_H^B}{\phi_L^A \phi_L^B} \;.
\end{equation}
%
Since it involves ERI's of type $\braket{AB}{AB}$ OEP's cannot be directly defined here.
However, Mulliken approximation allows one to express ERI's in terms of the
overlap and Coulomb integrals, i.e.,
%
\begin{equation}
 \braket{ij}{kl} \approx \frac{1}{4} S_{ij}S_{kl}
 \left[ \braket{ii}{kk} + \braket{ii}{ll} + \braket{jj}{kk} + \braket{jj}{ll}\right] \;.
\end{equation}
%
Application of the above approximation to Eq.~\eqref{e:v0-ct} yields
%
\begin{multline}\label{e:v0-ct.mulliken}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B}\right] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times \\
  \left[ r_{HL}^A + r_{HL}^B + \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
                             + \braket{\phi_L^A \phi_L^A}{\phi_H^B \phi_H^B}\right]  \;,
\end{multline}
%
where 
%
\begin{equation} 
 r_{HL}^X \equiv \braket{\phi_H^X \phi_H^X}{\phi_L^X \phi_L^X} \;.
\end{equation}
%
First of all, note that $r_{HL}^A$ and $r_{HL}^B$ are just constant numbers
associated with the isolated monomers and 
independent on the molecular aggregate. Also, the remaining four ERI's
can be considered as Coulombic interactions between HOMO and LUMO orbitals
of unperturbed molecular wavefunctions.
Then, applying distributed multipole expansion and truncating it on the monopole
one finds that
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_H^B \phi_H^B} \approx \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} \;,
\end{equation}
%
where the charge centroids of HOMO orbitals are given by
%
\begin{equation} 
 {\bf r}_H^X = \tbraket{\phi_H^X}{\hat{\bf r}}{\phi_H^X} \;.
\end{equation}
%
Note that, once occupied molecular orbitals are localized, the above approximation
should yield correct description. LUMO orbitals are usually not much localized.
Here, we use the distributed cumulative atomic charges to represent them, %cite CAMM paper
%
\begin{equation} 
 q^X_{x,L} =-\sum_{\alpha\in x} \sum_\beta S_{\alpha\beta} C_{\alpha L}^X C_{\beta L}^X
\end{equation}
%
and one can find that assuming this one obtains
%
\begin{equation} 
 \braket{\phi_L^A \phi_L^A}{\phi_L^B \phi_L^B} 
 \approx \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At}
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \;.
\end{equation}
%
The two remaining ERI's can be then approximated as follows:
%
\begin{equation} 
 \braket{\phi_H^A \phi_H^A}{\phi_L^B \phi_L^B} 
 \approx -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} \;,
\end{equation}
%
and similarly for the twin ERI. To summarize the derivation, the CT matrix element
is approximately given by
%
\begin{multline}\label{e:v0-ct.mulliken.working}
 V^{{\rm CT },(0)} \approx \frac{1}{2} S_{HL}^{AB} S_{LH}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\ 
 + \frac{1}{\vert {\bf r}_H^A - {\bf r}_H^B \vert} 
 + \sum_{x\in A}^{\rm At} \sum_{y\in B}^{\rm At} 
 \frac{q_{x;L}^A q_{y;L}^B}{\vert {\bf r}_x - {\bf r}_y \vert} \Big] \\
 -\frac{1}{4} S_{HH}^{AB} S_{LL}^{AB} \times 
  \Big[ r_{HL}^A + r_{HL}^B \\
 -\sum_{y\in B}^{\rm At}
 \frac{q_{y;L}^B}{\vert {\bf r}_H^A - {\bf r}_y \vert} 
 -\sum_{x\in A}^{\rm At}
 \frac{q_{x;L}^A}{\vert {\bf r}_H^B - {\bf r}_x \vert} \Big]\;.
\end{multline}
%
Thus, the computational cost of the above expression is negligible as
compared to the original formula in Eq.~\eqref{e:v0-ct}.

@@

Mulliken approximation can also be used to treat the pure exchange coupling (Eq.).
It is straightforward to show that
%
\begin{multline}\label{e:v0-exch-mulliken}
V^{{\rm Exch},(0)} \approx -\frac{1}{8} \sum_{\mu\nu\in A} \sum_{\lambda\sigma\in B} 
 P_{\nu\mu}^{g\rightarrow e(A)} P_{\lambda\sigma}^{g\rightarrow e(B)} 
 S_{\mu\lambda}  S_{\sigma\nu} \times \\
 \left[ \braket{\mu\mu}{\sigma\sigma} + \braket{\lambda\lambda}{\nu\nu} 
      + \braket{\mu\mu}{\nu\nu} + \braket{\lambda\lambda}{\sigma\sigma}\right] \;.
\end{multline}
%
However, ERI's that involve AO's in two different molecules can be safely neglected.
That leads to the following simplified expression:
%
\begin{multline}\label{e:v0-exch.mulliken.working}
V^{{\rm Exch},(0)} \approx 
  -\frac{1}{8} \Big\{ \sum_{\mu\nu\in A} P_{\nu\mu}^{g\rightarrow e(A)} G_{\mu\nu}^A
    [{\bf s}^{AB} {\bf P}^{g\rightarrow e(B)} {\bf s}^{BA} ]_{\mu\nu} \\
  + \sum_{\sigma\lambda\in B} P_{\lambda\sigma}^{g\rightarrow e(B)} G_{\lambda\sigma}^B
    [{\bf s}^{BA} {\bf P}^{g\rightarrow e(A)} {\bf s}^{AB} ]_{\sigma\lambda} 
  \Big\}
\end{multline}
%
with $G_{\mu\nu} \equiv \braket{\mu\mu}{\nu\nu}$. Note that $G_{\mu\nu}^A$ and $G_{\lambda\sigma}^B$
are just constant matrices that can be considered as effective fragment parameters.

@@

To summarize, the overall form of the OEP-TI/CIS model is still given as in the original TI/CIS model
by
%
\begin{equation}
  V \approx V^{\rm Direct} + V^{\rm Inirect} \;,
\end{equation}
%
where the direct and indirect coupling constants are respectively
%
\begin{subequations}
\begin{align}
  V^{\rm Direct  } &\equiv V^{\rm Coul} + V^{\rm Exch} + V^{\rm Ovrl} \;,\\
  V^{\rm Indirect} &\equiv V^{\rm TI-2} + V^{\rm TI-3} \;,
\end{align}
\end{subequations}
%
with
%
\begin{subequations}
\begin{align}
 V^{\rm TI-2} &\equiv-\frac{V^{\rm ET1} V^{\rm HT2}}{E_3-E_1} -\frac{V^{\rm ET2} V^{\rm HT1}}{E_4-E_1}  \;,\\
 V^{\rm TI-3} &\equiv \frac{V^{\rm CT} \left( V^{\rm ET1} V^{\rm ET2} + V^{\rm HT1} V^{\rm HT2}\right) }{(E_3-E_1)(E_4-E_1)} \;.
\end{align}
\end{subequations}
%
In the above, the direct EET coupling contributions are
%
\begin{subequations}\label{e:ovrl-direct}
\begin{align}
 V^{\rm Coul} &= \frac{V^{{\rm Coul},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Exch} &= \frac{V^{{\rm Exch},(0)}}{1 - S_{12}^2} \;, \\
 V^{\rm Ovrl} &=-\frac{(E_1+E_2)S_{12}}{2(1-S_{12}^2)}   \;.
\end{align}
\end{subequations}
%
whereas the indirect EET coupling is evaluated from
the overlap\hyp{}corrected ET, HT and CT matrix elements that read
%
\begin{equation}\label{e:ovrl-indirect}
 V^{\rm t} = \left[ 1 - S_{\rm t}^2 \right]^{-1} \left\{ V^{{\rm t},(0)} - \frac{1}{2} (E_1+E_2) S_{\rm t} \right\} \;,
\end{equation}
%
where `t' denotes one of the matrix element types (ET1, ET2, HT1, HT2, CT) 
and $S_{\rm t}$ is the appropriate overlap integral between basis states.

Despite the same general form,
the differences between the original Fujimoto's model and the newly derived OEP\hyp{}based model 
are significant:
%
\begin{enumerate}
 \item The Hamiltonian matrix elements are evaluated from the fragment effective 
parameters, for which only the one\hyp{}electron integrals are needed. Therefore, the computational
cost is significantly reduced as compared to the parent TI/CIS model. In particular, 
$V^{{\rm Coul},(0)}$ is evaluated by using the TrCAMM method developed previously,
$V^{{\rm Exch},(0)}$ and $V^{{\rm CT},(0)}$ are computed from the Mulliken approximated
formulae in Eqs.~\eqref{e:v0-exch.mulliken.working} and \eqref{e:v0-ct.mulliken.working}, respectively,
as well as $V^{\rm ET1}$, $V^{\rm ET2}$,
$V^{{\rm HT1},(0)}$ and $V^{{\rm HT2},(0)}$ are treated by the generalized density fitting
with OEP effective matrices as effective parameters spanned in auxiliary AO basis set 
(Eqs.~\eqref{e:v0-et1-oep}, \eqref{e:v0-et2-oep}, \eqref{e:v0-ht1-oep}, \eqref{e:v0-ht2-oep}
and Eqs.~\eqref{e:a:voep}-\eqref{e:a:aoep}). Note that evaluation
of Eqs.~\eqref{e:ovrl-direct} and \eqref{e:ovrl-indirect} 
is computationally inexpensive because it involves computing only approximate overlap
integrals between basis states;
 \item The relaxation effects due to the intermolecular interactions are not included
in the current OEP\hyp{}based model.
Note that in the original TI/CIS model the basis states and all the one\hyp{}particle density matrices are built from the
self\hyp{}consistently adjusted fragment densities according to the DFI method.
\end{enumerate}
%
%\paragraph*{Overlap corrections to the Hamiltonian.}
%Since in the TI/CIS method the basis states are constructed from the monomer wavefunctions,
%the overlap effects should be properly taken into account. It was reported previously
%that overlap correction to the $\left< \Phi_1 \vert \mathscr{H} \vert \Phi_2 \right>$ 
%matrix element brings negligible contributions to the 
%total EET coupling (c.f. the `overlap' contribution in Ref.). On the other hand,
%the importance of the overlap effects on the other off\hyp{}diagonal Hamiltonian matrix elements were not directly studied. 
%After the overlap correction, the constituents of the direct coupling take the form
%
%Since evaluation
%of Eqs.~\eqref{e:ovrl-direct} and \eqref{e:ovrl-indirect} 
%is computationally inexpensive, we shall consider the overlap\hyp{}corrected
%Hamiltonian in the present work.
